\bfseries Convolution-based nonlinear functions on tensor fields and tensor images

### 2022-09-21 paper/main.tex

% To-Do list:
% -----------
% - What are our GOALS!!?
%   -- one option: this formulation can express all equivariant differential operators discretized to a cubical d-torus. 
%   -- another option: can we produce a characterization of all equivariant functions (maybe based on invariants or these filters) that don't require the use of non-linearities.
%   -- another option: emulate cosmological simulations.
% - change N to N^3 in the appropriate locations; already done??
% - Understand what functions can and cannot be expressed on this model 
% - Extend it to non-linear maps (eg, by multiplications and contractions)
% - Should we be representing images in fourier space? Ask Leslie!
% - Understand the literature
%   -- Discretized vector calculus and differential geometry.
%   -- Group-equivariant CNNs; what's been done?
%   -- Understand how this formulation compares with steerable CNNs
%   -- What is known about what functions CNNs can represent? all linear translation equivariant functions can be written as convvolutions if the filters are as large as the image (simple observation)
% what about non-linear? is there a polynomial basis here? 
%  -- Define "local" functions, is there a characterization of functions that can be written as convolutions with small filters?
% - There is a one-indexing and zero-indexing issue. Should we be consistent?
% - Some definitions begin with "given" some with "let". Should we try to be more consistent?

% -- if the size of the filter is large enough, are we universal???? or can we express all polynomial functions? is there a version of Stone-Weierstrass for this?
% --- add the identity and levi civita in the possible output tensors
% --- define reordering of the indices
% --- we don't need to be in the torus and we don't need to be square (or cubical)
% --- generalize convolution to rectangular non-toroidal images

%-- is it the same to do convolutions + products + convolutions + products

%-- a counting argument may tell us that all the linear functions that are equivariant  (Molien's formula)

@@

% write the levi civita contraction
% write the procedure of which we make all linear functions from k tensor images to k' tensor images of the same size. 
% do we include a pooling move?

% how do we enumerate all tensor functions

% 1, 6, 22, 49, 87 d=3, n=1,3,7,9 (11N^2-24N+21)/8

@@

% stuff for framing figures
\usepackage[framemethod=tikz]{mdframed}
\usetikzlibrary{shadows}
\definecolor{captiongray}{HTML}{555555}
\mdfsetup{%
  innertopmargin=2ex,
  innerbottommargin=1.8ex,
  linecolor=captiongray,
  linewidth=0.5pt,
  roundcorner=5pt,
  shadow=true,
  shadowcolor=black!05,
  shadowsize=4pt
}

@@

Contemporary natural science teems with data sets that are images or lattices or grids of geometric objects.
These might be observations of intensities (scalars), magnetic fields (pseudovectors), or polarizations (2-tensors) on a surface or in a volume.
Or they might be the inputs or outputs of a simulation, in which the initial conditions or fields are specified on a regular grid.
Any lattice or grid of vectors or tensors can be seen as a generalization of the concept of an image, in which the intensity in each pixel is replaced with a geometric object (scalar, vector, pseudovector, tensor) in each pixel.
These objects are \emph{geometric} in the sense that they are defined in terms of their transformation properties under geometric operators such as rotation, translation, and reflection.
Thus there is a need for machine learning methods designed for \emph{geometric images}---lattices or grids of scalars, vectors, and tensors.
There are already countless applications of machine learning in contexts in which the input data are geometric images, including examples in essentially all natural-science disciplines (for example, CITE).

@@

\begin{definition}[$k$-$p$-tensors] \label{def.tensors}
We say that $v\in \mathbb R^d$ is a 1-$p$-tensor if $O(d)$ acts on $v$ via the action \eqref{eq.action}. 
If $v_i$ is a 1-$p_i$-tensor then $T:=v_{1}\otimes\ldots \otimes v_k$ is a rank-1 $k$-$p$-tensor, where $p=\sum_{i=1}^k p_i \mod 2$ and the action of $O(d)$ is defined as
\begin{align}
    g\cdot (v_{1}\otimes\ldots \otimes v_k) = (g\cdot v_1)\otimes \ldots \otimes (g\cdot v_k)
\end{align}
Higher rank $k$-$p$-tensors are defined as linear combinations of rank-1  $k$-$p$-tensors where the action of $O(d)$ is extended linearly.
\end{definition}
Typically we would make the parity $p$ be a bit (either 0 for even parity or 1 for odd parity) but in principle it can be any integer.

We note that in physics the 1-0-tensors are known as \emph{vectors}, the 1-1-tensors are known as \emph{pseudovectors}, the 0-0-tensors are known as \emph{scalars}, 0-1-tensors are known as \emph{pseudoscalars}, the $k$-1-tensors with $k\geq 2$ are known as \emph{pseudotensors}, and finally the $k$-0-tensors with $k\geq 2$ are the things that are commonly known as \emph{tensors}.

@@

SOLE: If the next definition is going to use ``the torus'' then we should say a few words about that up-front, or above in the image definition.

\begin{definition}[geometric convolution]
Let $A$ be a $k$-$p$-tensor image on the $d$-torus with side length $N$.
Let $C$ be a $k'$-$p'$-tensor image (filter) on $[-m, m]^d$ where $2m+1<N$.
The geometric convolution $A\ast C$ is a $(k+k')$-$(p+p')$-tensor image such that
\begin{equation}
    (A\ast C)(\bar\i) = \sum_{\bar a\in[-m, m]^d} A(\bar\i - \bar a)\otimes C(\bar a) ~,
\end{equation}
where $\bar\i - \bar a$ is the translation of $\bar\i$ by $\bar a$ on the $d$-torus pixel grid $(\mathbb Z / N\mathbb Z)^d$.
\end{definition}
This definition is on the torus. If you are not on the torus, just pad the image out with zero tensors of the corresponding order and parity.

@@

We conjecture that these rules will generate all possible second-degree monomial functions of the input image (SOLE SUBJECT TO SOME CONDITIONS) that meet the output requirements. A polynomial function of degree 2 can be constructed by linear combinations of these second-degree monomial functions along with all the linear functions that also produce $k'$-$p'$-tensor images of side length $N'$ (plus perhaps constant images).
Higher-degree monomials and polynomials can be made out of products of lower-degree monomials, by generalization of the above.

SOLE: THIS PARAGRAPH OR THESE IDEAS GO ELSEWHERE, I THINK.
The geometric convolutions of \secref{sec:convolution} are local linear operators that take as input geometric images, and produce as output geometric images.
They are local in the sense that, at every pixel $\bar\i$ of the output image $(A\ast C)$, the convolution only makes use of the pixels of $A$ within a small neighborhood of of $\bar\i$.
Because tensors can be multiplied together using the outer product, and contracted according to the tensor contractions defined in \secref{sec:convolution}, it is possible, by multiplication, to construct a family of \emph{nonlinear} local geometric operators that take as input geometric images and produce as output geometric images.
This family of nonlinear local operators will be equivariant to the group $G_d$ when the linear local operators of which they are composed are equivariant.

@@

Introduce the discrete group. Why discrete? SOLE: SEE TEXT BELOW FOR DEFINITIONS.

@@

\begin{definition}[Action of $B_d$ on $k$-$p$-tensors]
\begin{align}
g\cdot(v_1 \otimes \ldots \otimes v_k) &= \det(g)^p\,(g\cdot v_1)\otimes\ldots\otimes(g\cdot v_k)
\end{align}
And extend linearly
\end{definition}

This may seem familiar: The $k$-tensor and $k$-pseudotensor were defined by how they transform under the orthogonal group $O(d)$, and our group $B_d$ is a subgroup of the orthogonal group.

@@

In practice, a complete set of invariant $k'$-$p'$-tensor filters (filters $C$ such that $g\cdot C(g^{-1} \cdot a') = C(a')$) can be found by group averaging.
This works by building any set of linearly independent $k'$-$p'$-tensor filters (randomly or systematically), and then building, for each of these linearly independent filters $C$, a group-averaged filter $\bar{C}$ by
\begin{equation}
    \bar{C}(a') = \frac{1}{|B_d|}\,\sum_{g\in B_d} g\cdot C(g^{-1}\cdot a') ~,
\end{equation}
where $|B_d|$ is the number of group elements (8 for $d=2$ and 27 for $d=3$).
In detail we took a systematic (not random) approach that initialized the averaging with a set of independent $k'$-$p'$-tensor convolution filters that span the space of all possible geometric convolution filters at side length $M$ ($M=2\,m+1$) and dimension $d$.
There are $M^d\,d^{k'}$ independent filters in this initial set.
The averaged filters are then reduced to an ``eigen-set'' of orthogonal, non-zero filters by the singular-value decomposition.
The singular-value decomposition reduces the number of filters dramatically.
The outputs of the singular-value decomposition can be normalized however seems appropriate.
In detail we normalized to get unit tensor norms in the non-zero pixels.
The results of these operations are shown for $d=2$ and $m\in[1, 2]$ in \figref{fig:filters23} and \figref{fig:filters25}.
HOGG: Give a table saying how many filters there are for each tuple of $(d,m,k',p')$.
HOGG: Perhaps remind the reader that the code is available.
\begin{figure}[tp]
  \begin{mdframed}
  \color{captiongray}
  \begin{center}
\includegraphics[width=\textwidth]{notebooks/filter_2_3.png}
  \end{center}
\caption{All the filters for $d=2$, $m=1$ ($M=3$).
Notes: Scalars and pseudo-scalars are shown with signed colors; where there is no symbol in the box the value is zero. The $2$-$p'$-tensor filters are shown via the action of the tensor on an image of a letter ``R''; the transformation properties of the $2$-$p'$-filters are such that these filters may not look obviously invariant to rotations, but they are.
There are no invariant pseudoscalar ($0$-$1$-tensor) filters available at $(d,m) = (2,1)$.
Three of the $2$-$0$-tensors are duplicates of the $0$-$0$-tensor (scalar) filters but multiplied by the identity tensor; there is only one non-trivial invariant $2$-$0$-tensor filter.
We don't show the $k'$-$p'$-filters at $k'>2$ because we don't know how to visualize them (even the $k'=2$ case is sketchy).\label{fig:filters23}}
  \end{mdframed}
\end{figure}
\begin{figure}[tp]
  \begin{mdframed}
  \color{captiongray}
  \begin{center}
\includegraphics[width=\textwidth]{notebooks/filter_2_5.png}
  \end{center}
\caption{All the filters for $d=2$, $m=2$ ($M=5$).
Notes: Symbols and colors as in \figref{fig:filters23}.
We don't show the $2$-$p'$-tensor filters at $m=2$ because there are many of them.\label{fig:filters25}}
  \end{mdframed}
\end{figure}

@@

What do they look like? Like calculus operators! See figures.
\begin{figure}
  \begin{mdframed}
  \color{captiongray}
  \begin{center}
    \includegraphics[width=\textwidth]{notebooks/monomials_1.png}
  \end{center}
    \caption{A scalar image $s$ and convolutions with four chosen filters.}
  \end{mdframed}
\end{figure}

Now show contractions of products of the above on those images.

\begin{figure}
  \begin{mdframed}
  \color{captiongray}
  \begin{center}
    \includegraphics[width=\textwidth]{notebooks/monomials_2.png}
  \end{center}
    \caption{All unconvolved second-degree monomials of $s$, given four chosen filters. For the 2-tensor outputs (order $k=2$), we traced them back to scalars.}
  \end{mdframed}
\end{figure}

@@

\paragraph{Acknowlegements:}
It is a pleasure to thank Teresa Huang (JHU) and Kate Storey-Fisher (NYU) for valuable discussions.
This project made use of Python~3 \cite{python3}, numpy \cite{numpy}, matplotlib \cite{matplotlib}, and cmastro \cite{cmastro}.
All code used for making the data and figures in this paper are available at \url{https://github.com/davidwhogg/GeometricConvolutions}.

>>>>

% To-Do list:
% -----------
% - What are our GOALS!!?
%   -- one option: this formulation can express all equivariant differential operators discretized to a cubical d-torus. 
%   -- another option: can we produce a characterization of all equivariant functions (maybe based on invariants or these filters) that don't require the use of non-linearities.
% - Understand what functions can and cannot be expressed on this model 
% - Should we be representing images in fourier space? Ask Leslie!
% - Understand the literature
%   -- Discretized vector calculus and differential geometry.
%   -- Group-equivariant CNNs; what's been done?
%   -- Understand how this formulation compares with steerable CNNs
%   -- What is known about what functions CNNs can represent? all linear translation equivariant functions can be written as convvolutions if the filters are as large as the image (simple observation)
% what about non-linear? is there a polynomial basis here? 
%  -- Define "local" functions, is there a characterization of functions that can be written as convolutions with small filters?
% - There is a one-indexing and zero-indexing issue. Should we be consistent?
% - Some definitions begin with "given" some with "let". Should we try to be more consistent?
% add zeroth order monomials (constants, very few)
% --- we don't need to be in the torus and we don't need to be square (or cubical)

@@

% SOLEDAD: audit the levi civita contraction
%GIVE THE METHOD A NAME AND RUN THE NAME THROUGH THE DOCUMENT
%reformat the monomial figures to look like equations
%visualize the group $B_d$ at d=2
%make an introduction figure showing examples of geometric filters

% - HOGG: Change the aspect ratios of the figures so they can be put into talk slides :)

%pixel positions in images are 1-0-tensors and they transform as 1-0-tensors

%change the notation from k-p to k_p
%should we use the upper index notation??
%t

@@

% stuff for framing figures
\usepackage[framemethod=tikz]{mdframed}
\usetikzlibrary{shadows}
\definecolor{captiongray}{HTML}{555555}
\mdfsetup{%
  innertopmargin=2ex,
  innerbottommargin=1.8ex,
  linecolor=captiongray,
  linewidth=0.5pt,
  roundcorner=5pt,
  shadow=true,
  shadowcolor=black!05,
  shadowsize=4pt
}
\newenvironment{hoggfigure}{%
  \begin{figure}[tp]%
    \begin{mdframed}%
    \color{captiongray}}{%
    \end{mdframed}%
  \end{figure}}

@@

Contemporary natural science teems with data sets that are images or lattices or grids of geometric objects.
These might be observations of intensities (scalars), magnetic fields (pseudovectors), or polarizations (2-tensors) on a surface or in a volume.
Or they might be the inputs or outputs of a simulation, in which the initial conditions or fields are specified on a regular grid.
For examples, see \figref{fig:examples} and the caption thereto.
Any lattice or grid of vectors or tensors can be seen as a generalization of the concept of an image, in which the intensity in each pixel is replaced with a geometric object (scalar, vector, pseudovector, tensor) in each pixel.
These objects are \emph{geometric} in the sense that they are defined in terms of their transformation properties under geometric operators such as rotation, translation, and reflection.
Thus there is a need for machine learning methods designed for \emph{geometric images}---lattices or grids of scalars, vectors, and tensors.
There are already countless applications of machine learning in contexts in which the input data are geometric images, including examples in essentially all natural-science disciplines (HOGG CITE THINGS).
\begin{hoggfigure}
  \begin{center}
    \begin{minipage}[b]{2.5in}\noindent%
      \includegraphics[width=\textwidth]{jpegPIA18916.jpeg}\\
      \textsl{(a)} temperature and polarization
    \end{minipage}
    \begin{minipage}[b]{2in}\noindent%
      \includegraphics[width=\textwidth]{key_figures_197.pdf}\\
      \textsl{(b)} salinity and current
    \end{minipage}\\[2ex]
    \begin{minipage}[b]{2.5in}\noindent%
      \includegraphics[width=\textwidth]{applsci-09-02108-g001.png}\\
      \textsl{(c)} temperature
    \end{minipage}
    \begin{minipage}[b]{1.8in}\noindent%
      \includegraphics[width=\textwidth]{The-distribution-of-the-modified-potential-vorticity-at-the-850-K-potential-temperature.png}\\
      \textsl{(d)} vorticity
    \end{minipage}\\[2ex]
    \begin{minipage}[b]{1.9in}\noindent%
      \includegraphics[width=\textwidth]{FbAjqkkWAAANqFc.jpeg}\\
      \textsl{(e)} intensity and polarization
    \end{minipage}
    ~~\begin{minipage}[b]{2.5in}\noindent%
      \includegraphics[width=\textwidth]{41524.pdf}\\[1ex]
      \textsl{(f)} stress tensor
    \end{minipage}
  \end{center}
  \caption{Examples of geometric images in the natural sciences.
  \textsl{(a)}~A visualization of a temperature map and a polarization map from the ESA \textsl{Planck} Mission \cite{planck}.
  The color map shows a temperature field (a scalar or 0-0-tensor) on the sphere, and the whiskers show the principal eigenvector direction of a 2-0-tensor field in two dimensions.
  In detail the underlying data are represented on a pixel grid (healpixel \cite{healpix}) on the sphere.
  \textsl{(b)}~Some other stuff from \url{https://climatedataguide.ucar.edu/climate-data/godas-ncep-global-ocean-data-assimilation-system} HOGG EXPLAIN AND CITE.
  \textsl{(c)}~Some other stuff from \url{https://www.mdpi.com/2076-3417/9/10/2108/htm} HOGG EXPLAIN AND CITE.
  \textsl{(d)}~From \url{https://www.researchgate.net/figure/The-distribution-of-the-modified-potential-vorticity-at-the-850-K-potential-temperature_fig3_26635879}.
  \textsl{(e)}~Ask Jordy Davelaar (and thank him).
  \textsl{(f)}~From \url{https://www.nature.com/articles/s41524-019-0234-8}.
  \label{fig:examples}}
\end{hoggfigure}

@@

\begin{definition}[$k$-$p$-tensors]\label{def.tensors}
We say that $v\in \mathbb R^d$ is a 1-$p$-tensor if $O(d)$ acts on $v$ via the action \eqref{eq.action}. 
If $v_i$ is a 1-$p_i$-tensor then $T:=v_{1}\otimes\ldots \otimes v_k$ is a rank-1 $k$-$p$-tensor, where $p=\sum_{i=1}^k p_i \mod 2$ and the action of $O(d)$ is defined as
\begin{align}
    g\cdot (v_{1}\otimes\ldots \otimes v_k) = (g\cdot v_1)\otimes \ldots \otimes (g\cdot v_k)
\end{align}
Higher rank $k$-$p$-tensors are defined as linear combinations of rank-1  $k$-$p$-tensors where the action of $O(d)$ is extended linearly.
\end{definition}
Typically we would make the parity $p$ be a bit (either 0 for even parity or 1 for odd parity) but in principle it can be any integer.

We note that in physics the 1-0-tensors are known as \emph{vectors}, the 1-1-tensors are known as \emph{pseudovectors}, the 0-0-tensors are known as \emph{scalars}, 0-1-tensors are known as \emph{pseudoscalars}, the $k$-1-tensors with $k\geq 2$ are known as \emph{pseudotensors}, and finally the $k$-0-tensors with $k\geq 2$ are the things that are commonly known as \emph{tensors}.
In general, any $k$-$p$-tensor $a$ can be written as a sum of outer products of order-$1$ ($k=1$) tensors (vectors and pseudovectors), where each term in the sum is an outer product of $k$ order-$1$ tensors and the parity $p$ is the sum of the parities of the input order-$1$ tensors (mod 2, perhaps).

@@

\begin{definition}[geometric convolution]
Let $A$ be a $k$-$p$-tensor image on the $d$-torus with side length $N$.
Let $C$ be a $k'$-$p'$-tensor image (filter) on $[-m, m]^d$ where $2m+1<N$.
The geometric convolution $A\ast C$ is a $(k+k')$-$(p+p')$-tensor image such that
\begin{equation}
    (A\ast C)(\bar\i) = \sum_{\bar a\in[-m, m]^d} A(\bar\i - \bar a)\otimes C(\bar a) ~,
\end{equation}
where $\bar\i - \bar a$ is the translation of $\bar\i$ by $\bar a$ on the $d$-torus pixel grid $(\mathbb Z / N\mathbb Z)^d$.
\end{definition}
This definition is on the torus. If you the image is not on the torus, we can pad the image out with zero tensors of the corresponding order and parity.

@@

We conjecture that these rules will generate all possible second-degree monomial functions of the input image as long as the filter size is sufficiently large (BEN, is this correct?). A polynomial function of degree 2 can be constructed by linear combinations of these second-degree monomial functions along with all the linear functions that also produce $k'$-$p'$-tensor images of side length $N'$ (plus perhaps constant images).
Higher-degree monomials and polynomials can be made out of products of lower-degree monomials, by generalization of the above.

The geometric convolutions of \secref{sec:convolution} are local linear operators that take as input geometric images, and produce as output geometric images.
They are local in the sense that, at every pixel $\bar\i$ of the output image $(A\ast C)$, the convolution only makes use of the pixels of $A$ within a small neighborhood of of $\bar\i$.
Because tensors can be multiplied together using the outer product, and contracted according to the tensor contractions defined in \secref{sec:convolution}, it is possible, by multiplication, to construct a family of \emph{nonlinear} local geometric operators that take as input geometric images and produce as output geometric images.
This family of nonlinear local operators will be equivariant to the group $G_d$ when the linear local operators of which they are composed are equivariant.

@@

Convolutional filters are widely used in machine learning for scalar images. The fundamental property of these operators are that they are translation equivariant, and that every translation equivariant linear function can be expressed as a convolution with a fixed filter (as long as the filter can be set to be as large as the image). The same property holds for geometry images.

\begin{theorem}
A function $f:\mathcal A_{N,d,k,p}\to A_{N,d, k'', p''}$ is a linear translation equivariant linear function if and only if it is the convolution with a geometric filter $k'$-$p'$-tensor filter $C$ with possibly sidelength $N$, where $k+k'=k''$ and $p+p'=p''$.
\end{theorem}

\begin{proof}
TO DO.
\end{proof}

In addition to translation symmetries, we want to consider other natural symmetries occurring in the application domains where vectors and tensors arise. Ideally we would like to apply continuous rotations to the images, but their discretized nature makes it challenging. Recent work has proposed an approach to approximate continuous symmetries \cite{} that require interpolating and cropping the images. Here, for simplicity we focus on discrete rotations as in \cite{}, and we extend the group action to the geometric objects in the images.

@@

Not that the action of $B_d$ is a subgroup of $O(d)$, therefore the action of $B_d$ on $k$-$p$-tensors is the restriction of the action in Definition \ref{def.tensors} to the subgroup.

@@

In practice, a complete set of invariant $k'$-$p'$-tensor filters (filters $C$ such that $g\cdot C(g^{-1} \cdot a') = C(a')$) can be found by group averaging.
This works by, for each setting of order $k'$ and parity $p'$, building a collection of linearly independent $k'$-$p'$-tensor filters (randomly or systematically), and then building, for each of these linearly independent filters $C$, a group-averaged filter $\bar{C}$ by
\begin{equation}
    \bar{C}(a') = \frac{1}{|B_d|}\,\sum_{g\in B_d} g\cdot C(g^{-1}\cdot a') ~,
\end{equation}
where $|B_d|$ is the number of group elements (8 for $d=2$ and 27 for $d=3$).
In detail we took a systematic (not random) approach that, for each setting of $(k',p')$, initialized the averaging with a set of independent $k'$-$p'$-tensor convolution filters that span the space of all possible geometric convolution filters at side length $M$ ($M=2\,m+1$) and dimension $d$.
There are $M^d\,d^{k'}$ independent filters in this initial set.
The averaged filters are then reduced to an ``eigen-set'' of orthogonal, non-zero filters by the singular-value decomposition.
The singular-value decomposition reduces the number of filters dramatically.
The outputs of the singular-value decomposition can be normalized however seems appropriate.
In detail we normalized to get unit tensor norms in the non-zero pixels.
The results of these operations are shown for $d=2$ and $m\in[1, 2]$ in \figref{fig:filters23} and \figref{fig:filters25}.
HOGG: Give a table saying how many filters there are for each tuple of $(d,m,k',p')$.
HOGG: Perhaps remind the reader that the code is available.
\begin{hoggfigure}
  \begin{center}
\includegraphics[width=\textwidth]{notebooks/filter_2_3.png}
  \end{center}
\caption{All the filters for $d=2$, $m=1$ ($M=3$), $k'\in [0,1,2]$.
Notes: Scalars and pseudo-scalars are shown with signed colors; where there is no symbol in the box the value is zero. The $2$-$p'$-tensor filters are shown via the action of the tensor on an image of a letter ``R''; the transformation properties of the $2$-$p'$-filters are such that these filters may not look obviously invariant to rotations, but they are.
There are no invariant pseudoscalar ($0$-$1$-tensor) filters available at $(d,m) = (2,1)$.
Three of the $2$-$0$-tensors are duplicates of the $0$-$0$-tensor (scalar) filters but multiplied by the identity tensor; there is only one non-trivial invariant $2$-$0$-tensor filter.
We don't show the $k'$-$p'$-filters at $k'>2$ because we don't know how to visualize them (even the $k'=2$ case is sketchy).
Note that the vector ($1$-$0$-tensor) filters look like pure divergence and the pseudovector ($1$-$1$-tensor) filters look like pure curl.\label{fig:filters23}}
\end{hoggfigure}
\begin{hoggfigure}
  \begin{center}
\includegraphics[width=\textwidth]{notebooks/filter_2_5.png}
  \end{center}
\caption{All the filters for $d=2$, $m=2$ ($M=5$), $k'\in [0,1]$.
Notes: Symbols and colors as in \figref{fig:filters23}.
We don't show the $2$-$p'$-tensor filters at $m=2$ because there are many of them.
At $(d,m)=(2,2)$ a pseudoscalar filter appears.
Again, the vector and pseudovectors look like pure divergence and pure curl, respectively.\label{fig:filters25}}
\end{hoggfigure}

@@

What do they look like? Like calculus operators! See figures.
\begin{hoggfigure}
  \begin{center}
    \includegraphics[width=\textwidth]{notebooks/monomials_1.png}
  \end{center}
  \caption{A scalar image $s$ and convolutions with four chosen filters.}
\end{hoggfigure}

Now show contractions of products of the above on those images.
\begin{hoggfigure}
  \begin{center}
    \includegraphics[width=\textwidth]{notebooks/monomials_2.png}
  \end{center}
  \caption{All unconvolved second-degree monomials of $s$, given four chosen filters. For the 2-tensor outputs (order $k=2$), we traced them back to scalars.}
\end{hoggfigure}

@@

We could have added the determinant operation and eigenvalues.....

\paragraph{Acknowlegements:}
It is a pleasure to thank
Leslie Greengard (Flatiron),
Teresa Huang (JHU), and
Kate Storey-Fisher (NYU) for valuable discussions.
This project made use of Python~3 \cite{python3}, numpy \cite{numpy}, matplotlib \cite{matplotlib}, and cmastro \cite{cmastro}.
All code used for making the data and figures in this paper are available at \url{https://github.com/davidwhogg/GeometricConvolutions}.
